---
output: github_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(
  fig.path = "man/figures/", 
  fig.width = 7, 
  fig.height = 7, 
  dpi = 300
)
```

# plasmapR

<!-- badges: start -->
  [![Codecov test coverage](https://codecov.io/gh/bradyajohnston/plasmapR/branch/main/graph/badge.svg)](https://app.codecov.io/gh/bradyajohnston/plasmapR?branch=main)
  [![R-CMD-check](https://github.com/bradyajohnston/plasmapR/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/bradyajohnston/plasmapR/actions/workflows/R-CMD-check.yaml)
  <!-- badges: end -->


This is an R package for making plasmid maps using `{ggplot2}`.

## Installation 

> This package is still very early in development and the API may change. The 
> parser for `.gb` files works most of the time but has not been tested 
> extensively.

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("bradyajohnston/plasmapr")
```


## Example

`plasmapR` provides functions for parsing and plotting .gb plasmid files. 

Once a plasmid has been exported in Genbank format it can be parsed and plotted.

```{r example-plasmid, dev='ragg_png'}
# library(plasmapR)
library(ggplot2)
fl <- system.file('extdata', 'petm20.gb', package = "plasmapR")

plasmid <- read_gb(fl)
dat <- as.data.frame(plasmid)

dat[-1, ] |> 
  ggplot(aes(start=start, end = end, group = index, direction=direction), middle = 3) + 
  geom_hline(yintercept = 4) +
  geom_feature_arrow(aes(fill = type), width = 0.2, head_size = 100) + 
  scale_x_continuous(limits = c(0, plasmid$length)) +
  coord_polar() + 
  scale_y_continuous(limits = c(0,5)) + 
  theme_minimal()
```


Access the features by turning the plasmid into a data.frame.
```{r}
fl <- system.file('extdata', 'petm20.gb', package = "plasmapR")

plasmid <- fl |> 
  read_gb()

dat <- plasmid |> 
  as.data.frame()

head(dat)


dat[dat$type == "CDS", ] |> 
  plot_plasmid(name = "pETM-20")
```

It's not currently intended for linear display, but it can be used as such. I recommend checking out the [`gggenese`](https://wilkox.org/gggenes/) package.

```{r}
#| fig-height: 3
#| message: false
#| warning: false
dat[dat$type == "CDS", ] |> 
  plot_plasmid(name = NULL) + 
  ggplot2::coord_cartesian() + 
  ggplot2::scale_y_continuous(limits = NULL)
```


## A {ggplot2} Object

The result of the call is just a {ggplot2} plot, which you can further customise 
to your liking with themes, etc.
```{r example-theme, dev='ragg_png'}
fl <- system.file('extdata', '20.gb', package = "plasmapR")

plt <- fl |> 
  read_gb() |> 
  plot_plasmid()

plt + ggplot2::theme_bw()
```

